\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{hyperref}
\usepackage{fontawesome}
\input{glyphtounicode}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
      \small#5 & \small #6 \\
    \end{tabular*}\vspace{-3pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-3pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\large$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Abu Bakkar Siddiq} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+14695880435}{+1-469-588-0435}
    $|$
    \faAt \hspace{.5pt} \href{mailto:piashsiddiq@gmail.com}{piashsiddiq@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/abu-siddiq-bakkar/}{LinkedIN}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/piashsiddiq}{GitHub}
   
\end{center}

%------------Summary------------
 \vspace{-20pt}
\section{Summary}
 \vspace{-5pt}
\resumeItemListStart \resumeItem {\textbf{Actively seeking full-time roles in Accounting, Finance, and Business/Data Analytics.}} 
  \vspace{-5pt}
\resumeItem{9+ years of experience in financial reporting, general ledger accounting, ERP operations (SAP S/4HANA, Oracle ERP), cost control, variance analysis, budgeting, and business analytics.}  
 \vspace{-5pt}
 \resumeItem{CPA Candidate pursuing a Dual MS in Accounting Analytics and Business Analytics \& Artificial Intelligence at The University of Texas at Dallas; submitted Application of Intent (AOI) to the Texas State Board of Public Accountancy (TSBPA) for CPA exam eligibility evaluation.} 
\vspace{-5pt}
\resumeItem{Adept at bridging traditional accounting functions with data analytics and AI-driven tools (Power BI, Tableau, SQL, Python, R) to improve reporting accuracy and operational efficiency.}
\vspace{-10pt}\resumeItemListEnd

\section{Education}
  \vspace{-3pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {Dual Degree -- MS in Accounting Analytics \& MS in Business Analytics and AI
      }{Jan 2025 \textbf{--} Dec 2026 (Expected)}
      {The University of Texas at Dallas, Dallas, TX, USA}{}
      {}{}
      \vspace{-20pt}
    \resumeEducationHeading
      {Master of Business Studies (MBS) -- Accounting
      }{Sept. 2016}
      {National University of Bangladesh}{}
      {}{}
      \vspace{-20pt}
    \resumeEducationHeading
      {Bachelor of Business Studies (BBS) -- Accounting
      }{Jan. 2015}
      {National University of Bangladesh}{}
      {}{}
    \resumeSubHeadingListEnd
%----------- SKILLS -----------
  \vspace{-30pt}
\section{Skills}
  \vspace{-3pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Accounting \& ERP Systems:}{ SAP S/4HANA, Oracle ERP, QuickBooks, Tally, Advanced Excel (Pivot Tables, Power Query, Power Pivot, VLOOKUP/XLOOKUP, SUMIFS, INDEX-MATCH)} \\
        \textbf{Data Analytics \& Visualization:}{ Power BI, Tableau, SQL, Python, R} \\
        \textbf{Certifications:}{ SAP -- Foundations of Business Analysis; Intuit -- Bookkeeping Basics \& Financial Statement Analysis; Microsoft -- Power BI \& Data Analysis with Excel; Coursera -- Python for Data Visualization; IBM -- Generative AI Applications; DataCamp -- Business Data in SQL}
        
    }}
  \resumeSubHeadingListEnd
\vspace{-15pt}
\section{Professional Experience}
  \vspace{-3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Executive -- Accounts, Finance \& MIS}{January 2022 \textbf{--} January 2025} 
      {Square Fashions Limited}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Operated SAP S/4HANA for end-to-end financial transaction processing, including general and adjusting journal entries, and generated financial statements (Income Statement, Balance Sheet).}
        \resumeItem{Developed interactive Power BI dashboards for sales vs. target tracking and Accounts Receivable aging analysis, improving visibility into collection performance.}
        \resumeItem{Conducted job costing, profitability analysis, overhead cost analysis, and cash flow analysis, optimizing contribution margin by 12\% through data-driven pricing and cost control strategies.}
        \resumeItem{Supported SAP S/4HANA ERP implementation by facilitating team training on system workflows, increasing team productivity and process efficiency by 20\%.}
      \resumeItemListEnd
    \vspace{-5pt}

    \resumeSubheading
      {Senior Executive -- Accounts \& Finance}{November 2018 \textbf{--} December 2021}
      {Al-Madina Pharmaceuticals Limited}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Prepared and analyzed monthly sales performance reports, bank reconciliations, collection reports, and vendor management summaries, delivering financial reports to support senior management decisions.}
        \resumeItem{Performed operational overhead variance analysis using Power Query and Excel Solver, reducing operational costs by 10\% through process optimization.}
        \resumeItem{Conducted physical inventory audits and stock aging analysis, reducing stock discrepancies by 15\% and strengthening inventory control accuracy.}
      \resumeItemListEnd
    \vspace{-5pt}

    \resumeSubheading
      {Executive -- Accounts \& Audit}{January 2016 \textbf{--} October 2018}
      {Novo Healthcare \& Pharma Limited}{Dhaka, Bangladesh}
      \resumeItemListStart
        \resumeItem{Managed full-cycle Accounts Receivable and Accounts Payable processes in QuickBooks, including journal entries, payment processing, bank reconciliation, and vendor/creditor reconciliations.}
        \resumeItem{Developed integrated sales and collection reports for depot accounting using Advanced Excel, redesigned the receivables aging system, and improved collections tracking efficiency by 10\%.}
        \resumeItem{Participated in semi-annual internal audits alongside the audit team, verifying accuracy of financial reports, reconciliations, and compliance with internal controls.}
      \resumeItemListEnd

    \vspace{-3pt}  

  \resumeSubHeadingListEnd

\vspace{-10pt}
\section{Academic Project Experience}
\vspace{-3pt}
\textbf{Course: Business Analytics with R} \hfill Jan 2025 \textbf{--} May 2025
\resumeSubHeadingListStart

 \resumeProjectHeading
  {\textbf{Predicting Credit Card Fraud}}{}
\resumeItemListStart
  \resumeItem{Built and compared three ML classification models (Logistic Regression, Decision Tree, k-NN) in R on a dataset of 284,807 transactions, achieving 97\%+ accuracy using SMOTE for class imbalance and ROC/AUC for model evaluation.}
  \resumeItem{Identified that 0.5 percent of fraudulent transactions clustered around low-dollar amounts during late-night hours in online and point-of-sale retail channels, informing actionable real-time fraud alert thresholds.}
  \resumeItem{Tools: R (caret, ggplot2, dplyr, ROSE), SMOTE, CRISP-DM methodology.}
\resumeItemListEnd
\resumeSubHeadingListEnd


    %----------- Publications -----------

\section{Publications}
\vspace{-3pt}
R. Ramezani and A. B. Siddiq, "A Business Analytics Framework for Credit Card Fraud Detection and Risk Profiling," Journal of Financial Crime, under review (submitted June 2026).

    

%-------------------------------------------
\end{document}
